The Eclipse Integrated Computational Environment

### 2018-07-12 src/main.tex
Fixed typos and errors in the references. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>
Addressed all reviews and finished grammatical edits. Signed-off-by: Jay Jay Billings <billingsjj@ornl.gov>

\address{$^{1}$Computer Science and Mathematics Division, Oak Ridge National
Laboratory, Oak Ridge, TN 37830, USA}
\address{$^{2}$The Bredesen Center for Interdisciplinary Research and Graduate
Education, University of Tennessee, 444 Greve Hall, 821 Volunteer
  Blvd. Knoxville, TN 37996-3394}
\address{$^{3}$University of Washington, Seattle, WA 98105}
\address{$^{4}$General Electric Company, 3200 North Grandview Blvd Waukesha, WI
53188-1678}
\address{$^{5}$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
\address{$^{6}$Kichwa Coders Ltd. 1 Plomer Green Avenue Downley, High Wycombe
HP13 5LN United Kingdom}
\address{$^{7}$Northwestern University 633 Clark Street Evanston, IL 60208}
\address{$^{8}$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
CA 94720}
\address{$^{9}$Department of Computer Science, and Department of Biological
Sciences, Purdue University, West Lafayette, IN 47906} 
\address{$^{10}$Acato Information Management, LLC 114 Union Valley Rd. Oak Ridge,
TN 37830}
\address{$^{11}$Colorado State University Fort Collins, CO 80523}

@@

Problems in modeling and simulation require significantly different
workflow management technologies than standard grid-based workflow
management systems. Computational scientists typically interact with
simulation software in a feedback-driven way where solutions and
workflows are developed iteratively and simultaneously. This work
describes common activities in workflows and how combinations of these
activities form unique workflows. It presents the Eclipse Integrated
Computational Environment as a workflow management system and
development environment for the modeling and simulation community.
Examples of the Environment's applicability to problems in energy
science, general multiphysics simulations, quantum computing, and other
areas are presented along with its impact on the community at large.

@@

This manuscript has been authored by UT-Battelle, LLC under Contract No.
DEAC05-00OR22725 with the U.S. Department of Energy. The United States
Government retains and the publisher, by accepting the article for
publication, acknowledges that the United States Government retains a
nonexclusive, paid-up, irrevocable, world-wide license to publish or
reproduce the published form of this manuscript, or allow others to do
so, for United States Government purposes. The Department of Energy will
provide public access to these results of federally sponsored research
in accordance with the DOE Public Access Plan
(http://energy.gov/downloads/doe-public-access-plan ).

>>>>

\address{$^{1}$Computer Science and Mathematics Division, Oak Ridge National
Laboratory, Oak Ridge, TN 37830, USA}
\address{$^{2}$The Bredesen Center for Interdisciplinary Research and Graduate
Education, University of Tennessee, 444 Greve Hall, 821 Volunteer
  Blvd. Knoxville, TN 37996-3394}
\address{$^{3}$University of Washington, Seattle, WA 98105}
\address{$^{4}$General Electric Company, 3200 North Grandview Blvd Waukesha, WI
53188-1678}
\address{$^{5}$Georgia Institute of Technology North Avenue, Atlanta, GA 30332}
\address{$^{6}$Kichwa Coders Ltd., 1 Plomer Green Avenue Downley, High Wycombe
HP13 5LN United Kingdom}
\address{$^{7}$Northwestern University, 633 Clark Street Evanston, IL 60208}
\address{$^{8}$Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley,
CA 94720}
\address{$^{9}$Department of Computer Science and Department of Biological
Sciences, Purdue University, West Lafayette, IN 47906} 
\address{$^{10}$Acato Information Management, LLC, 114 Union Valley Rd., Oak Ridge,
TN 37830}
\address{$^{11}$Colorado State University, Fort Collins, CO 80523}

@@

Problems in modeling and simulation require significantly different
workflow management technologies from standard grid-based workflow
management systems. Computational scientists typically interact with
simulation software in a feedback-driven way where solutions and
workflows are developed iteratively and simultaneously. This work
describes common modeling and simulation activities in workflows and how combinations of these
activities form unique workflows. It presents the Eclipse Integrated
Computational Environment as a workflow management system and
development environment for the modeling and simulation community.
Examples of the Environment's applicability to problems in energy
science, general multiphysics simulations, quantum computing, and other
areas are presented along with its impact on the community at large.

@@

This manuscript has been authored by UT-Battelle, LLC, under contract DE-AC05-00OR22725 with the US Department of Energy (DOE). The US government retains and the publisher, by accepting the article for publication, acknowledges that the US government retains a nonexclusive, paid-up, irrevocable, worldwide license to publish or reproduce the published form of this manuscript, or allow others to do so, for US government purposes. DOE will provide public access to these results of federally sponsored research in accordance with the DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).
